Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-18 paper/ijcai/paper.tex
statements vs components vs slice fixed

\subsection{Combining \sfl{} and \cs{}}
\label{sec:comb}
\Sof{@todo: define slicer - set of statements}
To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

@@

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious classes, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
  \item\label{step:group} Assemble all the resulting slicers of each failing test; 
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices of each failing test obtained in Step~\ref{step:group} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables identification of statements in the spectra
whose values can be set to zero, \ie{}, the components marked with $0$
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the running example,
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

>>>>

\subsection{Combining \sfl{} and \cs{}}
\label{sec:comb}

To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

@@

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. \comb{} uses a granularity of statements.
First, the combined technique picks statements $c_4$ and $c_3$, which 
appear at the top of the ranking, for further analysis. 
(The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code. A slice is a
set of statements. Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes statements $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious classes, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
  \item\label{step:group} Assemble all the resulting slicers of each failing test; 
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices of each failing test obtained in Step~\ref{step:group} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables the identification of statements in the spectra
whose values can be set to zero, \ie{}, the components marked with $0$
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the running example,
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.
